---
title: "Annotation Package for *Heterorhabditis bacteriophora*"
author: "Lalson Wesly Johnson"
date: "`r Sys.Date()`"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Annotation Package for Heterorhabditis bacteriophora}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

This package provides annotation data for the *Heterorhabditis bacteriophora* organism. It includes gene information, functional annotations, and kegg pathway information derived from the Wormbase Parasite and various other biological databases.
```{r eval=FALSE}
# Installation
if (!requireNamespace("BiocManager", quietly = TRUE)) {
  install.packages("BiocManager")
}
BiocManager::install(version = "devel")
if (!requireNamespace("AnnotationHub", quietly = TRUE)) {
  install.packages("AnnotationHub")
}
```

## Loading packages
```{r}
# Loading the Package
library(AnnotationHub)
```

```{r}
# Installing the org.Hbacteriophora.eg.db package
ah <- AnnotationHub()
org.Hbacteriophora.eg.db <- ah[["AH121717"]]
```

## Supported key types
```{r keytypes}
# List all supported key types
keytypes(org.Hbacteriophora.eg.db)
```

## Accessing Gene Information
```{r genes}
# Accessing Gene Information
keys <- head(keys(org.Hbacteriophora.eg.db, 
                  keytype = "GID")) # Get sample gene IDs
select(org.Hbacteriophora.eg.db, 
       keys = keys, 
       columns = c("GENENAME", "SYMBOL"), 
       keytype = "GID")
```

## Querying GO Terms
```{r gos}
# Querying GO Terms
select(org.Hbacteriophora.eg.db, 
       keys = keys, 
       columns = c("GO", "ONTOLOGY"), 
       keytype = "GID")
```

## Extracting GO terms for Biological Process
```{r go_terms}
# Extracting GO terms for Biological Process
select(org.Hbacteriophora.eg.db, 
       keys = keys, 
       columns = c("GO", "ONTOLOGY"), 
       keytype = "GID") %>%
  dplyr::filter(ONTOLOGY == "BP")
```
## Querying KEGG Pathway Information
```{r kegg}
# Querying KEGG Pathway Information
select(org.Hbacteriophora.eg.db, 
       keys = keys, 
       columns = "KEGGPATHWAY", 
       keytype = "GID")
```

## Session Info
```{r session}
sessionInfo()
```

