---
title: "Annotation Package for Heterorhabditis bacteriophora"
author: "Lalson Wesly Johnson"
date: "`r Sys.Date()`"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Annotation Package for Heterorhabditis bacteriophora}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This package provides annotation data for the *Heterorhabditis bacteriophora* organism. It includes gene information, functional annotations, and kegg pathway information derived from the Wormbase Parasite and various other biological databases.
```{r eval=FALSE}
# Installation
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("org.Hbacteriophora.eg.db")
```

## Loading packages
```{r eval=FALSE}
#Loading the Package
library(org.Hbacteriophora.eg.db)
library(magrittr)
```
## Supported key types
```{r eval=FALSE}
# List all supported key types
keytypes(org.Hbacteriophora.eg.db)
```

## Accessing Gene Information
```{r eval=FALSE}
#Accessing Gene Information
keys <- head(keys(org.Hbacteriophora.eg.db, keytype="GID"))  # Get sample gene IDs
select(org.Hbacteriophora.eg.db, keys=keys, columns=c("GENENAME", "SYMBOL"), keytype="GID")
```

## Querying GO Terms
```{r eval=FALSE}
#Querying GO Terms
select(org.Hbacteriophora.eg.db, keys=keys, columns=c("GO", "ONTOLOGY"), keytype="GID")
```

## Extracting GO terms for Biological Process
```{r eval=FALSE}
# Extracting GO terms for Biological Process
select(org.Hbacteriophora.eg.db, keys=keys, columns=c("GO", "ONTOLOGY"), keytype="GID") %>%
  dplyr::filter(ONTOLOGY == "BP")
```
## Querying KEGG Pathway Information
```{r eval=FALSE}
# Querying KEGG Pathway Information
select(org.Hbacteriophora.eg.db, keys=keys, columns="KEGGPATHWAY", keytype="GID")
```

## Session Info
```{r}
sessionInfo()
```

